Main Analysis

### 2024-06-18 Manuscript Analysis/main_analysis.Rmd
created additional pupil figures

@@

@@

@@

ggsave("Figures/difference_plots_speakers.png", plot = diff_plot_1, scale = 1.8)

>>>>

```
```{r}

m2_predicted_values |>
  dplyr::filter(rep_acc == "accurate") |>
  ggplot() +
  aes(x = time_norm,
      y = fit,
      color = speaker,
      fill = speaker,
      linetype = speaker) +
  geom_ribbon(aes(ymin = ul, ymax = ll), alpha = .5, color = NA) +
  geom_line() +
  geom_vline(xintercept = 0, size = 0.35) +
  geom_vline(xintercept = 1910, linetype = 2) +
  annotate("rect", xmin = 500, xmax = 2910, ymin = 0, ymax = 200, alpha = 0.15) +
  coord_cartesian(ylim = c(-10, 250), xlim = c(0, 4910)) +
  theme_bw() +
  theme(aspect.ratio = 1,
        legend.position = "bottom",
        plot.title = element_text(hjust = 0.5)) +
  labs(x = "Normalized Time (ms)",
       y = "Pupil Dilation (Arbitrary Units)",
       title = "ALS vs Neurotypical Speaker",
       color = "Speaker",
       fill = "Speaker",
       linetype = "Speaker") +
  scale_color_manual(values = c(my_pal[1], my_pal[5]), labels = c("Neurotypical", "ALS")) +
  scale_fill_manual(values = c(my_pal[1], my_pal[5]), labels = c("Neurotypical", "ALS")) +
  scale_linetype_manual(values = c("solid", "dashed"), labels = c("Neurotypical", "ALS"))

ggsave("Figures/pupil_model_speakers.png", plot = last_plot())

@@

```{r}

m2_predicted_values |>
  dplyr::filter(speaker == "Control") |>
  ggplot() +
  aes(x = time_norm,
      y = fit,
      linetype = rep_acc) +
  geom_ribbon(aes(ymin = ul, ymax = ll), alpha = .5, fill = my_pal[1], color = NA) +
  geom_line(color = my_pal[1]) +
  geom_vline(xintercept = 0, size = 0.35) +
  geom_vline(xintercept = 1910, linetype = 2) +
  annotate("rect", xmin = 500, xmax = 2910, ymin = 0, ymax = 200, alpha = 0.15) +
  coord_cartesian(ylim = c(-10, 250), xlim = c(0, 4910)) +
  theme_bw() +
  theme(aspect.ratio = 1,
        legend.position = "bottom",
        plot.title = element_text(hjust = 0.5)) +
  labs(x = "Normalized Time (ms)",
       y = "Pupil Dilation (Arbitrary Units)",
       title = "Neurotypical Speaker",
       linetype = "Repetition Accuracy") +
  scale_linetype_manual(values = c("solid", "twodash"))

ggsave("Figures/pupil_model_control.png", plot = last_plot())

@@

```{r}

m2_predicted_values |>
  dplyr::filter(speaker == "ALS") |>
  ggplot() +
  aes(x = time_norm,
      y = fit,
      linetype = rep_acc) +
  geom_ribbon(aes(ymin = ul, ymax = ll), alpha = .5, fill = my_pal[5], color = NA) +
  geom_line(color = my_pal[5]) +
  geom_vline(xintercept = 0, size = 0.35) +
  geom_vline(xintercept = 1910, linetype = 2) +
  annotate("rect", xmin = 500, xmax = 2910, ymin = 0, ymax = 200, alpha = 0.15) +
  coord_cartesian(ylim = c(-10, 250), xlim = c(0, 4910)) +
  theme_bw() +
  theme(aspect.ratio = 1,
        legend.position = "bottom",
        plot.title = element_text(hjust = 0.5)) +
  labs(x = "Normalized Time (ms)",
       y = "Pupil Dilation (Arbitrary Units)",
       title = "ALS Speaker",
       linetype = "Repetition Accuracy") +
  scale_linetype_manual(values = c("solid", "twodash"))

ggsave("Figures/pupil_model_ALS.png", plot = last_plot())

@@

ggsave("Figures/difference_plots_speakers.png", plot = diff_plot_1, scale = .8)

ggsave("Figures/difference_plots_control.png", plot = diff_plot_2, scale = .8)

ggsave("Figures/difference_plots_ALS.png", plot = diff_plot_3, scale = .8)
